### 2016-06-07 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor formatting edits and rounded tabulated HRRs in gas burner report

% \multirow{16}{*}{\large{\textbf{A4}}}
%  & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
%  & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
%  & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
%  & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
%  & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
%  & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
%  & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
%  & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
% \cline{2-4}
%  & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
%  & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
%  & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
%  & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
%  & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
%  & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
%  & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
%  & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\

@@

\subsection{Measurement Uncertainty}
\label{sec:Uncertainty}
There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity, and heat release rate measurements. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$). For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

\subsubsection{Compartment Dimensions}
Each length measurement was taken carefully. Length measurements such as the room dimensions and instrumentation array locations were made with a hand held laser measurement device, which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}. However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range. Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}. Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$^{\circ}$C at $277^{\circ}$C and increases to $\pm$9.5$^{\circ}$C at $871^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15\%.

\subsubsection{Heat Flux Gauges}
Total heat flux measurements were made with water-cooled Schimidt-Bolter gauges. The manufacturer reports a $\pm$3\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}. Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$8\%~\cite{Pitts:2006}.

\subsubsection{Gas Sampling}
The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1\% when compared with span gas volume fractions~\cite{Bundy:2007}. Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12\% is associated with gas concentration measurements~\cite{Lock:1}.

\subsubsection{Pressure Transducers}
Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers. The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1\%~\cite{Setra:2002}. The total expanded uncertainty was estimated at 10\%.

\subsubsection{Bi-Directional Probes}
Bi-directional probes and single thermocouples were used to measure the velocity. The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above. A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe. The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath. A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}. The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$18\%.

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2\%~\cite{Romet:2014}. The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm??$\%. ***\textit{Still need to finish reviewing literature about HRR uncertainty and add description here about calculation and uncertainty estimate.}***

@@

\begin{table}[!ht]
\caption{Heat Release Rates for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 901 & 634 & 330 \\
Test 3 				& 326 & 650	& 905 & 631 & 326 \\
Test 4				& 351 & 654	& 952 & 652 & 337 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:15	&	12:45	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Heat Release Rates for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
Test 22				&     	764 	  \\
Test 23				&     	789 	  \\
Test 24				& 	    789 	  \\
Test 25				&     	786 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

@@

\subsection{Measurement Uncertainty}
\label{sec:Uncertainty}
There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity, and heat release rate measurements. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100~\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$). For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

\subsubsection{Compartment Dimensions}
Each length measurement was taken carefully. Length measurements such as the room dimensions and instrumentation array locations were made with a hand held laser measurement device, which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}. However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range. Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}. Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0~\%.

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.

\subsubsection{Heat Flux Gauges}
Total heat flux measurements were made with water-cooled Schimidt-Bolter gauges. The manufacturer reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}. Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.

\subsubsection{Gas Sampling}
The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}. Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12~\% is associated with gas concentration measurements~\cite{Lock:1}.

\subsubsection{Pressure Transducers}
Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers. The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1~\%~\cite{Setra:2002}. The total expanded uncertainty was estimated at 10~\%.

\subsubsection{Bi-Directional Probes}
Bi-directional probes and single thermocouples were used to measure the velocity. The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above. A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe. The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath. A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}. The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$18~\%.

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2~\%~\cite{Romet:2014}. The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm15$~\%. ***\textit{Still need to finish reviewing literature about HRR uncertainty and add description here about calculation and uncertainty estimate.}***

@@

\begin{table}[!ht]
\caption{Heat Release Rates for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
% Original Values
% Test 2 				& 338 & 651	& 901 & 634 & 330 \\
% Test 3 				& 326 & 650	& 905 & 631 & 326 \\
% Test 4				& 351 & 654	& 952 & 652 & 337 \\
% Rounded Values
Test 2 				& 340 & 650	& 900 & 630 & 330 \\
Test 3 				& 330 & 650	& 910 & 630 & 330 \\
Test 4				& 350 & 650	& 950 & 650 & 337 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
% Original Values
% Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
% Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
% Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
% Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
% Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
% Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
% Rounded Values
Test 5 - Seq. 1		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{710} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Old table layout --- will delete soon
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Old table layout --- will delete soon
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:15	&	12:45	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Heat Release Rates for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
% Original Values
% Test 22				&     	764 	  \\
% Test 23				&     	789 	  \\
% Test 24				& 	    789 	  \\
% Test 25				&     	786 	  \\
% Rounded Values
Test 22				&     	760 	  \\
Test 23				&     	790 	  \\
Test 24				& 	    790 	  \\
Test 25				&     	790 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	% Old table layout --- will delete soon
	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	% Old table layout --- will delete soon
	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier
